Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-03-08 rmd/suppl_info.Rmd
edit: one-patch sim

---
output:
  pdf_document:
    toc: true
    latex_engine: xelatex
    includes:
      before_body: title.tex
mainfont: Times New Roman
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
fontsize: 11pt
header-includes:
  - \usepackage{amsmath, fancyhdr, caption, booktabs}
  - \pagestyle{fancy}
  - \renewcommand{\headrulewidth}{0pt}
  - \pagenumbering{gobble}
---

@@

We performed one-patch simulations to identify parameter combinations that allow stable coexistence of the three species without dispersal and disturbance. Specifically, we varied attack rates $a_{ij}$, handling time $h_{ij}$, intrinsic growth rate of the basal species $r_b$, and carrying capacity $K$. First, we considered `r nrow(dplyr::distinct(df_sim1, r_b, k, a1, h))` discrete combinations of $a_{BC}$, $r_b$, $K$, and $h$ (assumed $h_{ij} = h$). We further crossed `r nrow(dplyr::distinct(df_sim1, a2))` values of $a_{BP}$ (`r min(df_sim1$a2)` -- `r max(df_sim1$a2)` with an equal interval) and $a_{CP}$ (`r min(df_sim1$a3)` -- `r max(df_sim1$a3)`), resulting in `r nrow(dplyr::distinct(df_sim1, a2, a3))` combinations. Consequently, we had a total of `r nrow(dplyr::distinct(df_sim1, r_b, k, a1, a2, a3, h))` combinations (`r nrow(dplyr::distinct(df_sim1, r_b, k, a1, h))` $\times$ `r nrow(dplyr::distinct(df_sim1, a2, a3))`) for one-patch simulations.

>>>>

---
output:
  pdf_document:
    toc: false
    latex_engine: xelatex
    includes:
      before_body: title.tex
mainfont: Times New Roman
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
fontsize: 11pt
header-includes:
  - \usepackage{amsmath, fancyhdr, caption, booktabs}
  - \pagestyle{fancy}
  - \renewcommand{\headrulewidth}{0pt}
  - \pagenumbering{gobble}
  - \setlength{\headheight}{14pt}
---

@@

We performed one-patch simulations to identify parameter combinations that allow stable coexistence of the three species without dispersal and disturbance. Specifically, we varied attack rates $a_{ij}$, handling time $h_{ij}$, intrinsic growth rate of the basal species $r_b$, and carrying capacity $K$. First, we considered `r nrow(dplyr::distinct(df_sim1, r_b, k, a1, h))` discrete combinations of $a_{BC}$, $r_b$, $K$, and $h$ (assumed $h_{ij} = h$). We further crossed `r nrow(dplyr::distinct(df_sim1, a2))` values of $a_{BP}$ (`r min(df_sim1$a2)` -- `r max(df_sim1$a2)` with an equal interval) and $a_{CP}$ (`r min(df_sim1$a3)` -- `r max(df_sim1$a3)`), resulting in `r nrow(dplyr::distinct(df_sim1, a2, a3))` combinations. Consequently, we had a total of `r nrow(dplyr::distinct(df_sim1, r_b, k, a1, a2, a3, h))` combinations (`r nrow(dplyr::distinct(df_sim1, r_b, k, a1, h))` $\times$ `r nrow(dplyr::distinct(df_sim1, a2, a3))`) for one-patch simulations. Note that we set the switching parmeter $s = 0$ if $a_{BP} = 0$, otherwise $s = 1$. Parameter values were summarized in **Table S1**.
